Bumble bee competition revisited under global climate change

### 2020-05-25 manuscript_v2.Rmd
draft 2 of intro

---
title: "Bumble bee competition revisited under global climate change"
author:
- Douglas B. Sponsler
- Fabrice Requier
- Katharina Kallnik
- Alice Claßen
- A. Fabienne Maihoff
- Ingolf Steffan-Dewenter
output:
  word_document:
    reference_docx: docx_template.docx
  pdf_document: default
bibliography: refs.bib
---

@@

The nascent reality of climate change has already revealed the fragile contingency of ecological paradigms that rely on the implicit assumption of climate stability [@Hannah2002-nv; @Walther2002-mq]. Thus, one of the central questions facing ecologists today is how climate change will affect the future fitness and distribution of species and, thereby, the composition and function of ecological communities. While it is intuitive that climate change should affect species and communities through environmental filtering, it is now recognized that climate change can also restructure biotic interactions [@Tylianakis2008-fi], such as competition and facilitation [@Ettinger2017-pk], altering the fitness landscape that governs community assembly and species coexistence [@Chesson2000-aw].

Bumble bees (Hymenoptera: *Bombus* spp.) have become a model system for the study of biotic interactions in ecological communities. In particular, the broad and overlapping distributions of bumble bee species, together with their gross similarity in morphology, behavior, and dietary niche, have attracted the attention of researchers interested in questions of interspecific competition and, more broadly, the rules of community assembly and species coexistence [@Plowright1984-lc; @Goulson2008-zy]. In this regard, however, bumble bees have proven somewhat enigmatic. On the one hand, there is evidence that resource limitation can be a significant constraint on local bumble populations [@Heinrich1976-wc; @Bowers1985-df], and certain bumble bee communties have been shown to be over-dispersed in terms of tongue length (a matching trait corresponding to floral corolla depth) or phyologeny (understood to encompass unmeasured trait variation), providing evidence for competition as a community assembly process [e.g. @Inouye1977-kl; @Pellissier2013-pk]. Nevertheless, bumble bee communities with an apparent excess of species richness and deficit of trait (or phylogenetic) dispersion are commonly observed [@Ranta1981-vx]. To account for this inconsistency, @Ranta1981-vx proposed that bumble bees communities are governed by a spatiotemporally heterogeneous mosaic of competitive conditions, such that competitive inequalities between species are sufficiently variable to allow more species to coexist than predicted by trait-based competition models. A complementary explanation, based on the core/satellite species hypothesis [@Hanski1982-hs], is that competitive forces are significant only among regionally abundant and widespread "core species", and the effects of competition are more pronounced in the structure of regional species pools than in that of local assemblages [@Hanski1982-xd].

As pointed out by @Williams1989-vr, however, the question of competition as a biogeographic/evolutionary-scale driver of communty assembly differs from that of competition as a local/behavioral-scale driver of species' interactions. While the role of competition in bumble bee community assembly remains somewhat obscure, there is broad empirical evidence that bumble bees facultatively partition resources to minimize competition [e.g @Inouye1978-qi; @Morse1982-bh; @Ishii2013-sm; @Brosi2013-mu; @Brosi2017-oc]. This distinction between spatiotemporal scales of competition, echoing the logic of @Ranta1981-vx, becomes especially important when the scope of inquiry switches from retrospective to prospective, and all the more so when there is reason to think that the ecological context of competition is undergoing rapid and unprecedented change. Since the height of bumble bee competition research in the 1980s, such a shift has indeed occurred, with retrospective questions of community assembly eclipsed by the urgency of conservation in the face of global changes in climate and land use [@Goulson2010-lo]. Given the uncertain spatiotemporal lags and exogenous drivers of community assembly, inferring the past role of competition through the study of bumble bee community structure may be of limited use in predicting the future fitness and distribution of bumble bee species. In this regard, the study of competition via behavioral patterns of floral resource partitioning that respond in real-time to variation in ecological context [@Spiesman2016-nf] provides a vital complement to the classical study of community assembly.

The study of competition as a behavioral phenomenon, however, is empirically and analytically demanding, since species interactions, not merely community composition, must be measured and interpreted. The difficulty is compounded when the goal is to infer the effects of environmental variation, since observations must be replicated across gradients of interest while minimizing the influence of confounding spatial or temporal effects. An elegant solution to both these challenges is the use of species interaction networks along steep elevation gradients [e.g. @Hoiss2015-gv; @Albrecht2018-gn]. Interaction network analysis provides a tractable framework for the study of resource partitioning [@Bluthgen2006-if], and steep elevation gradients can serve as space-for-time proxies in the study of climate effects, capturing a broad range of climate variation while minimizing the confounding effects of geographic distance [@Blois2013-wr]. To our knowledge, however, the analysis of plant-pollinator interaction networks along elevational climate gradients has never been applied specifically to the question of competition in bumble bees and its relation to climate change.

In this study, we analyze patterns of resource partitioning among bumble bees along an elevation gradient in the Berchtesgadener Alps of southeastern Germany. Our analysis has a hierarchical structure. First, we test the hypothesis that competition is of negligible significance in our study system. At least two plausible mechanisms can be proposed that would account for a lack of competition in bumble bee communities [@Ranta1981-vx]. First, it is possible that a super-abundance of floral resources could saturate the foraging capacity of a local bumble bee population. Indeed, this may be a common (though transient) phenomenon associated with the bloom of mass flowering crops, such as red clover [@Ranta1981-vx] and oilseed rape [@Westphal2009-sb]. Alternatively, competition could be attenuated if abiotic stress, such as low temperature, suppresses bumble bee populations below competition-inducing densities. This pattern would be a prediction of the "stress-gradient hypothesis" [@Bertness1994-zx], and while it has not, to our knowledge, been documented for bumble bees specifically, a recent study of whole bee communities in the Berchtesgaden system (of which bumble bees were a part) found evidence of dampened competition at high elevation sites along a montane-to-alpine gradient [@Hoiss2012-sn]. Under either mechanism, the most straightforward prediction is that bumble bee population density would be decoupled from resource density, since the latter would be non-limiting. For the same reason, the absence of competition would also predict that resource partitioning would be constrained only by trait-matching, not by niche overlap; thus, niche partitioning among species with similar traits should not exceed that predicted by a random null model.

Where the hypothesis of no competition can be rejected, we seek to differentiate inter- from intraspecific competition. These two forms of competition share the necessary precondition of resource limitation, but they imply distinct predictions regarding resource partitioning and trait-matching. Resource partitioning by bumble bees is mediated by variation in matching traits, the most well-studied of these being tongue length. Bumble bee tongue lengths vary between species, and the efficiency with which a bumble bee can collect nectar from a given flower depends largely on the closeness of match between the tongue length of the bee and the corolla depth of the flower [@Inouye1980-mv; @Ranta1980-ok]. Since tongue length also varies within species, and literature values for a given species vary, it is common to average available values and bin species into tongue-length "guilds" [@Pellissier2013-pk].

Where interspecific competition is strong, a species' dietary specialization should increase in proportion to the density of other species within the same tongue length guild per density of floral resources shared by that guild (hereafter referred to as "guild-packing"). Moreover, species within a tongue length guild should tend to exhibit divergent abundance dynamics, since they are reciprocally limiting. Under the pressure of intraspecific competition, however, individuals may respond by foraging more opportunistically within the constraints of their fundamental niche space []. Alternatively, a species may relieve intraspecific competition by subdividing, on the basis of intraspecific trait heterogeneity, into differently specialized populations [@Araujo2008-bp]. In either case, the species-level effect would be an increase in realized niche breadth (i.e. a decrease in specialization) in proportion to conspecific-packing (density of conspecifics per density of guild-level floral resources) [though see @Parent2014-hx].

These hypotheses and predictions are summarized in Table 1.

+--------------------------------+--------------------------------------------------------+
| Hypothesis                     | Prediction                                             |
+================================+========================================================+
| H1: No competition             | 1. BB density !~ FL density                            |
+--------------------------------+--------------------------------------------------------+
| H2a: Interspecific competition | 1. specialization ~ guild-packing                      |
|                                | 2. within-guild abundance divergence                   | 
+--------------------------------+--------------------------------------------------------+
| H2b: Intraspecific competition | 1. specialization ~ 1/conspecific-packing              |
|                                | 2. trait-matching ~ 1/conspecific-packing              |
+--------------------------------+--------------------------------------------------------+

**Table 1:** Hypothesized competitive processes with empirical predictions. BB = bumble bee; FL = floral. \

In this context, we formulate a "metahypothesis" concerning the variation of hypothesized competition processes through elevation and time (**Figure 1**). Consistent with the stress-gradient hypothesis [@Bertness1994-zx] and with previous empirical work in our study system [@Hoiss2012-sn], we hypothesize an inverse relationship between competition and elevation. Along a temporal axis, we hypothesize that the strength of competition is structured by the seasonal life history pattern of bumble bee colonies [@Goulson2010-lo]. During the solitary phase, when the bumble bee community consists only of foundress queens, competition should be low. Both inter- and intraspecific competition should intensify as colonies increase in size during the social phase. After the switch point, when colonies begin producing gynes and males instead of workers, intraspecific comeptition should decrease due to the strong morphological differences between queens, males, and workers within each species, but interspecific competition might intensify due to the effective "over-packing" of trait space wih the introduction of multiple morphological castes per species.

*Seasonal-Elevational metahypothesis.*    That any of the processes hypothesized above should obtain universally is both empirically and theoretically doubtful [@Ranta1981-vx]. More plausibly, which of these processes prevails -- and which species are favored by the prevailing process -- vary in both space and time, and this heterogenity of process could explain the structural idiosyncrasies of observed bumble bee communities [@Ranta1981-vx]. Rather than viewing this heterogeneity as an obstacle to inferring some universal rule of bumble bee community assembly, our aim in the present study is to investigate the heterogeneity itself as an ecological phenomenon, characterizing the variation in competitive processes (or lack thereof) in bumble bee communities through time and space.

```{r echo = FALSE, fig.cap = "**Figure 1:** Hypothesized variation in prevailing competitive processes through time and elevation."}
Time <- c(0,1,2,3)
Elevation <- c(0,1,2,3)
tab <- cbind(Time, Elevation) %>%
  as_tibble()

ggplot(tab, aes(Time, Elevation)) +
  geom_vline(xintercept = c(1,2), color = "white") +
  geom_hline(yintercept = c(1,2), color = "white") +
  scale_x_continuous(expand = c(0,0),
                     breaks = c(0.5, 1.5, 2.5), 
                     labels = c("founding", "build-up", "reproductive"),
                     limits = c(0,3)) +
  scale_y_continuous(expand = c(0,0),
                     breaks = c(0.5, 1.5, 2.5), 
                     labels = c("low", "mid", "high"),
                     limits = c(0,3)) +
  #geom_text() +
  annotate("text", x = 0.5, y = 2.5, label = "H1") +
  annotate("text", x = 1.5, y = 2.5, label = "H1") +
  annotate("text", x = 2.5, y = 2.5, label = "H1") +
  annotate("text", x = 0.5, y = 1.5, label = "H1") +
  annotate("text", x = 0.5, y = 0.5, label = "H1") +
  annotate("text", x = 1.5, y = 1.5, label = "H2 | H3") +
  annotate("text", x = 2.5, y = 1.5, label = "H2 < H3") +
  annotate("text", x = 1.5, y = 0.5, label = "H2 | H3") +
  annotate("text", x = 2.5, y = 0.5, label = "H2 < H3") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```
\

@@

<!-- - Look for divergent population trajectories of species as evidence of competition with temporal lag on effects -->
<!-- - Where does network analysis fit in? A legit question -- no need to jump right to fancy network metrics if simpler approaches work. But so far, none of my empirical predictions involve network metrics.  -->

@@

>>>>

---
title: "Bumble bee competition revisited under global climate change"
author:
- Douglas B. Sponsler
- Fabrice Requier
- Katharina Kallnik
- Alice Claßen
- A. Fabienne Maihoff
- Ingolf Steffan-Dewenter
output:
  pdf_document: default
  word_document:
    reference_docx: docx_template.docx
bibliography: refs.bib
---

@@

The nascent reality of climate change has already revealed the fragile contingency of ecological paradigms that rely on the assumption of climate stability [@Hannah2002-nv; @Walther2002-mq]. Thus, one of the central questions facing ecologists today is how climate change will affect the future fitness and distribution of species and, thereby, the composition and function of ecological communities. While it is intuitive that climate change should affect species and communities through environmental filtering, it is now recognized that climate change can also restructure biotic interactions [@Tylianakis2008-fi], such as competition and facilitation [@Ettinger2017-pk], altering the fitness landscape that governs community assembly and species coexistence [@Chesson2000-aw].

Bumble bees (Hymenoptera: *Bombus* spp.) have become a model system for the study of biotic interactions in ecological communities. In particular, the broad and overlapping distributions of bumble bee species, together with their gross similarity in morphology, behavior, and dietary niche, have attracted the attention of researchers interested in questions of interspecific competition and, more broadly, the rules of community assembly and species coexistence [@Plowright1984-lc; @Goulson2008-zy]. In this regard, however, bumble bees have proven somewhat enigmatic. On the one hand, there is evidence that resource limitation can be a significant constraint on local bumble populations [@Heinrich1976-wc; @Bowers1985-df], and certain bumble bee communities have been shown to be over-dispersed in terms of tongue length (a matching trait corresponding to floral corolla depth) or phyloogeny (understood to encompass unmeasured trait variation), providing evidence for competition as a community assembly process [e.g. @Inouye1977-kl; @Pellissier2013-pk]. Nevertheless, bumble bee communities with an apparent excess of species richness and deficit of trait (or phylogenetic) dispersion are commonly observed [@Ranta1981-vx]. To account for this inconsistency, @Ranta1981-vx proposed that bumble bees communities are governed by a spatiotemporally heterogeneous mosaic of competitive conditions, such that competitive inequalities between species are sufficiently variable to allow more species to coexist than predicted by trait-based competition models. A complementary explanation, based on the core/satellite species hypothesis [@Hanski1982-hs], is that competitive forces are significant only among regionally abundant and widespread "core species", and the effects of competition are more pronounced in the structure of regional species pools than in that of local assemblages [@Hanski1982-xd].

As pointed out by @Williams1989-vr, however, the question of competition as a biogeographic/evolutionary-scale driver of community assembly differs from that of competition as a local/behavioral-scale driver of species' interactions. While the role of competition in bumble bee community assembly remains somewhat obscure, there is broad empirical evidence that bumble bees facultatively partition resources to minimize competition [e.g @Inouye1978-qi; @Morse1982-bh; @Ishii2013-sm; @Brosi2013-mu; @Brosi2017-oc]. This distinction between spatiotemporal scales of competition, echoing the logic of @Ranta1981-vx, becomes especially important when the scope of inquiry switches from retrospective to prospective, and all the more so when there is reason to think that the ecological context of competition is undergoing rapid and unprecedented change. Since the height of bumble bee competition research in the 1980s, such a shift has indeed occurred, with retrospective questions of community assembly all but eclipsed by the urgency of conservation in the face of global changes in climate and land use [@Goulson2010-lo]. Given the uncertain spatiotemporal lags and exogenous drivers of community assembly, inferring the past role of competition through the study of bumble bee community structure may be of limited use in predicting the future fitness and distribution of bumble bee species. In this regard, the study of competition via behavioral patterns of floral resource partitioning that respond in real-time to variation in ecological context [@Spiesman2016-nf] provides a vital complement to the classical study of community assembly.

The study of competition as a behavioral phenomenon, however, is empirically and analytically demanding, since species interactions, not merely community composition, must be measured and interpreted. The difficulty is compounded when the goal is to infer the effects of climate variation, since observations must be replicated across gradients of interest while minimizing the influence of confounding spatial or temporal effects. An elegant solution to both these challenges is the use of species interaction network analysis along steep elevation gradients [e.g. @Hoiss2015-gv; @Albrecht2018-gn]. Interaction network analysis provides a tractable framework for the study of resource partitioning [@Bluthgen2006-if], and steep elevation gradients can serve as space-for-time proxies in the study of climate effects, capturing a broad range of climate variation while minimizing the confounding effects of geographic distance [@Blois2013-wr].

Previous studies of pollinator and plant communities along elevation gradients have tended to find decreased specialization and/or increased niche overlap at high elevation, which is often interpreted as an indication of reduced interspecific competition, though other mechanisms cannot be excluded [@Hoiss2012-sn; @Miller-Struttmann2014-wz; @Hoiss2015-gv; @Classen2020-nh]. If, in fact, competition in pollinator communities is attenuated at high elevation, this would be broadly consistent with the "stress-gradient hypothesis", which posits that prevailing biotic interactions shift from negative (e.g. competition) to positive (e.g. facilitation) along ascending gradients of environmental stress [@Bertness1994-zx]. As applied to pollinator communities, the logic would be that environmental stresses at high elevation, such as low temperatures and short growing seasons, suppress pollinator densities more strongly than the densities of their shared resources, thus causing a per-capita increase in food availability and a corresponding relaxation of competition.

In this study, we analyze patterns of resource partitioning in a bumble- bee-wildflower network sampled along an elevation gradient in the Berchtesgadener Alps of southeastern Germany. We first analyze species-level and group-level metrics of specialization and niche overlap to determine whether the bumble bees in our study system exihibit the expected pattern of decreased specialization and increased niche overlap at high elevation. To evaluate the plausibility of intepreting specialization and niche overlap as indices of competition, we then use independent floral surveying data to determine whether observed patterns in specialization and niche overlap correspond to variation in per-capita resource availability. Finally, we use the within-year temporal resolution of our dataset to test for reciprocal population dynamics of species within sites as a direct indication of interspecific competition. From these results, we derive predictions concerning the effects of climate change on competition as a constraint on bumble bee species and communities.

@@

@@

<!-- Our analysis has a hierarchical structure. First, we test the hypothesis that competition is of negligible significance in our study system. At least two plausible mechanisms can be proposed that would account for a lack of competition in bumble bee communities [@Ranta1981-vx]. First, it is possible that a super-abundance of floral resources could saturate the foraging capacity of a local bumble bee population. Indeed, this may be a common (though transient) phenomenon associated with the bloom of mass flowering crops, such as red clover [@Ranta1981-vx] and oilseed rape [@Westphal2009-sb]. Alternatively, competition could be attenuated if abiotic stress, such as low temperature, suppresses bumble bee populations below competition-inducing densities. This pattern would be a prediction of the "stress-gradient hypothesis" [@Bertness1994-zx], and while it has not, to our knowledge, been documented for bumble bees specifically, a recent study of whole bee communities in the Berchtesgaden system (of which bumble bees were a part) found evidence of dampened competition at high elevation sites along a montane-to-alpine gradient [@Hoiss2012-sn]. Under either mechanism, the most straightforward prediction is that bumble bee population density would be decoupled from resource density, since the latter would be non-limiting. For the same reason, the absence of competition would also predict that resource partitioning would be constrained only by trait-matching, not by niche overlap; thus, niche partitioning among species with similar traits should not exceed that predicted by a random null model.  -->

<!-- Where the hypothesis of no competition can be rejected, we seek to differentiate inter- from intraspecific competition. These two forms of competition share the necessary precondition of resource limitation, but they imply distinct predictions regarding resource partitioning and trait-matching. Resource partitioning by bumble bees is mediated by variation in matching traits, the most well-studied of these being tongue length. Bumble bee tongue lengths vary between species, and the efficiency with which a bumble bee can collect nectar from a given flower depends largely on the closeness of match between the tongue length of the bee and the corolla depth of the flower [@Inouye1980-mv; @Ranta1980-ok]. Since tongue length also varies within species, and literature values for a given species vary, it is common to average available values and bin species into tongue-length "guilds" [@Pellissier2013-pk]. -->

<!-- Where interspecific competition is strong, a species' dietary specialization should increase in proportion to the density of other species within the same tongue length guild per density of floral resources shared by that guild (hereafter referred to as "guild-packing"). Moreover, species within a tongue length guild should tend to exhibit divergent abundance dynamics, since they are reciprocally limiting. Under the pressure of intraspecific competition, however, individuals may respond by foraging more opportunistically within the constraints of their fundamental niche space []. Alternatively, a species may relieve intraspecific competition by subdividing, on the basis of intraspecific trait heterogeneity, into differently specialized populations [@Araujo2008-bp]. In either case, the species-level effect would be an increase in realized niche breadth (i.e. a decrease in specialization) in proportion to conspecific-packing (density of conspecifics per density of guild-level floral resources) [though see @Parent2014-hx].  -->

<!-- These hypotheses and predictions are summarized in Table 1. -->

<!-- +--------------------------------+--------------------------------------------------------+ -->
<!-- | Hypothesis                     | Prediction                                             | -->
<!-- +================================+========================================================+ -->
<!-- | H1: No competition             | 1. BB density !~ FL density                            | -->
<!-- +--------------------------------+--------------------------------------------------------+ -->
<!-- | H2a: Interspecific competition | 1. specialization ~ guild-packing                      | -->
<!-- |                                | 2. within-guild abundance divergence                   |  -->
<!-- +--------------------------------+--------------------------------------------------------+ -->
<!-- | H2b: Intraspecific competition | 1. specialization ~ 1/conspecific-packing              | -->
<!-- |                                | 2. trait-matching ~ 1/conspecific-packing              | -->
<!-- +--------------------------------+--------------------------------------------------------+ -->

<!-- **Table 1:** Hypothesized competitive processes with empirical predictions. BB = bumble bee; FL = floral. \ -->

<!-- In this context, we formulate a "metahypothesis" concerning the variation of hypothesized competition processes through elevation and time (**Figure 1**). Consistent with the stress-gradient hypothesis [@Bertness1994-zx] and with previous empirical work in our study system [@Hoiss2012-sn], we hypothesize an inverse relationship between competition and elevation. Along a temporal axis, we hypothesize that the strength of competition is structured by the seasonal life history pattern of bumble bee colonies [@Goulson2010-lo]. During the solitary phase, when the bumble bee community consists only of foundress queens, competition should be low. Both inter- and intraspecific competition should intensify as colonies increase in size during the social phase. After the switch point, when colonies begin producing gynes and males instead of workers, intraspecific comeptition should decrease due to the strong morphological differences between queens, males, and workers within each species, but interspecific competition might intensify due to the effective "over-packing" of trait space wih the introduction of multiple morphological castes per species.  -->

<!-- *Seasonal-Elevational metahypothesis.*    That any of the processes hypothesized above should obtain universally is both empirically and theoretically doubtful [@Ranta1981-vx]. More plausibly, which of these processes prevails -- and which species are favored by the prevailing process -- vary in both space and time, and this heterogenity of process could explain the structural idiosyncrasies of observed bumble bee communities [@Ranta1981-vx]. Rather than viewing this heterogeneity as an obstacle to inferring some universal rule of bumble bee community assembly, our aim in the present study is to investigate the heterogeneity itself as an ecological phenomenon, characterizing the variation in competitive processes (or lack thereof) in bumble bee communities through time and space.  -->

<!-- ```{r echo = FALSE, fig.cap = "**Figure 1:** Hypothesized variation in prevailing competitive processes through time and elevation."} -->
<!-- Time <- c(0,1,2,3) -->
<!-- Elevation <- c(0,1,2,3) -->
<!-- tab <- cbind(Time, Elevation) %>% -->
<!--   as_tibble() -->

<!-- ggplot(tab, aes(Time, Elevation)) + -->
<!--   geom_vline(xintercept = c(1,2), color = "white") + -->
<!--   geom_hline(yintercept = c(1,2), color = "white") + -->
<!--   scale_x_continuous(expand = c(0,0), -->
<!--                      breaks = c(0.5, 1.5, 2.5),  -->
<!--                      labels = c("founding", "build-up", "reproductive"), -->
<!--                      limits = c(0,3)) + -->
<!--   scale_y_continuous(expand = c(0,0), -->
<!--                      breaks = c(0.5, 1.5, 2.5),  -->
<!--                      labels = c("low", "mid", "high"), -->
<!--                      limits = c(0,3)) + -->
<!--   #geom_text() + -->
<!--   annotate("text", x = 0.5, y = 2.5, label = "H1") + -->
<!--   annotate("text", x = 1.5, y = 2.5, label = "H1") + -->
<!--   annotate("text", x = 2.5, y = 2.5, label = "H1") + -->
<!--   annotate("text", x = 0.5, y = 1.5, label = "H1") + -->
<!--   annotate("text", x = 0.5, y = 0.5, label = "H1") + -->
<!--   annotate("text", x = 1.5, y = 1.5, label = "H2 | H3") + -->
<!--   annotate("text", x = 2.5, y = 1.5, label = "H2 < H3") + -->
<!--   annotate("text", x = 1.5, y = 0.5, label = "H2 | H3") + -->
<!--   annotate("text", x = 2.5, y = 0.5, label = "H2 < H3") + -->
<!--   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) -->
<!-- ``` -->
<!-- \ -->
